Titeln på avhandlingens språk

### 2022-11-13 implications_optimization.tex
Update on Overleaf.
eq

Above, $\alpha, \beta$ and $C$ are constants which are responsible for modifying the objective function from one metric to another.
For instance, in the modeling used by \textcite{Moothedath2021EnergyOptimal,Moothedath2022EnergyEfficient,Moothedath2022Aperiodic}, the chosen characterization results in a metric which is equal to the energy penalty.
The outline of our solution that minimizes \cref{eq:epsilon_terminal} is provided below with the complete mathematical derivation in \cref{appx1}.

\bigskip

We first define an instantaneous sampling rate function $r(t)$ which is related to $\{t_n\}$ such that,
\begin{alignat}{1}
{\int_{t_{n-1}}^{t_n}}r(t)\dif t=1,\;\forall n\geq1\label{rt}
\end{alignat}
For instance, for periodic sampling, the rate function is a constant equal to the sampling frequency. 
% Using this rate function, we rewrite the expected number of samples as
% \begin{alignat}{1}
% \mathbb{E}[\mathcal{S}]&=\int_{t=0}^{\infty}\bigg(\!\int_{x=0}^{t}\!\!\!\!r(x)\,\mathrm{d}x\bigg)f_{\mathcal{T}}(t)\,\mathrm{d}t,\nonumber
% \end{alignat}
% and the approximate the expected wait time as
% \begin{alignat}{1}
% \mathbb{E}[\mathcal{W}]&=\int_{0}^{\infty}\dfrac{1}{2r(t)}f_\mathcal{T}(t)\,\mathrm{d}t.\nonumber
% \end{alignat}
Next, rewriting \cref{eq:epsilon_terminal} in terms of $r(t)$ and minimizing it gives as an optimum rate function $r^*(t)$ as
\begin{alignat}{1}
r^*(t)&=\sqrt{\dfrac{\beta f_\mathcal{T}(t)}{2\alpha\bar{F}_\mathcal{T}(t)}}\nonumber\\
\intertext{in turn resulting in, for a $\mathcal{T}$ distributed according to a Rayleigh distribution with parameter $\sigma$,}
r^*(t)&=\sqrt{\dfrac{\beta t}{2\alpha\sigma^2}}\nonumber\\
% \Rightarrow &\int_{t_n}^{t_{n+1}}\!\!\!\sqrt{\dfrac{\beta t}{2\alpha\sigma^2}}\,\mathrm{d}t=1,\;\forall n\geq1\nonumber\tag{from \eqref{rt}}\\
% \Rightarrow &\;t_{n+1}^{\frac{3}{2}}-t_{n}^{\frac{3}{2}}=3\sigma\!\sqrt{\tfrac{\alpha}{2\beta}}\nonumber\\
\Rightarrow t_n&=\Big(3\sigma\!\sqrt{\tfrac{\alpha}{2\beta}}\Big)^{\frac{2}{3}}n^{\frac{2}{3}}\label{tn_approx_rayleigh}
\end{alignat}

@@

However, an unconstrained optimization of the number of samples is trivial and meaningless as the solution points to a single sample at $t\!\rightarrow\!\infty$, which also takes the wait time to infinity.
We look at the constrained optimization of the expected number of samples with an upper bound $w_0$ for the expected wait.
That is, $\mathbb{E}[\mathcal{W}]\!\leq\!w_0$. We show in \cref{appx1} that the appropriate $\alpha$ and $\beta$ for this problem satisfy the condition
\begin{alignat}{1}\label{eq:optimization:sampling}
\frac{\alpha}{\beta}=\frac{2\sqrt{2}\,w_0^2}{(\mathlarger{\Gamma}(\tfrac{3}{4}))^2\,\sigma}\approx1.9\frac{w_0^2}{\sigma}
\end{alignat}
where, $\mathlarger{\Gamma}(x)$ is the Gamma function.

>>>>

Above, $\alpha, \beta$ and $C$ are constants which are responsible for modifying the objective function from one metric to another.
For instance, in the modeling used by \textcite{Moothedath2021EnergyOptimal,Moothedath2022EnergyEfficient,Moothedath2022Aperiodic}, the chosen characterization results in a metric which is equal to the energy penalty.
Our solution which minimizes \cref{eq:epsilon_terminal} is provided in \cref{tn_approx_rayleigh}.
It assumes a $\mathcal{T}$ distributed according to a Rayleigh distribution with parameter $\sigma$.
The complete mathematical derivation that leads to this formula is detailed in \cref{appx1}.

\begin{alignat}{1}
r^*(t)&=\sqrt{\dfrac{\beta t}{2\alpha\sigma^2}}\nonumber\\
\Rightarrow t_n&=\Big(3\sigma\!\sqrt{\tfrac{\alpha}{2\beta}}\Big)^{\frac{2}{3}}n^{\frac{2}{3}}\label{tn_approx_rayleigh}
\end{alignat}

@@

However, an unconstrained optimization of the number of samples is trivial and meaningless as the solution points to a single sample at $t\!\rightarrow\!\infty$, which also takes the wait time to infinity.
Thus, we look at the constrained optimization of the expected number of samples with an upper bound $w_0$ for the expected wait.
That is, $\mathbb{E}[\mathcal{W}]\!\leq\!w_0$. We show in \cref{appx1} that the appropriate $\alpha$ and $\beta$ for this problem satisfy the condition
\begin{alignat}{1}\label{eq:optimization:sampling}
\frac{\alpha}{\beta}=\frac{2\sqrt{2}\,w_0^2}{(\mathlarger{\Gamma}(\tfrac{3}{4}))^2\,\sigma}\approx1.9\frac{w_0^2}{\sigma}
\end{alignat}
where, $\mathlarger{\Gamma}(x)$ is the Gamma function.
